Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-06-12 paper-v1.tex
git

\paragraph{Inclusiveness via gamification.} ll the community is involved in the process of peer-reviewing since there is no selection process ('open participation', 'open interaction', 'open platform');

>>>>

\paragraph{Inclusiveness via gamification.} All the community is involved in the process of peer-reviewing since there is no selection process ('open participation', 'open interaction', 'open platform') and reviews evaluation are performed via Quadratic Voting.
